%-------------------------
% Resume in Latex
% Author : Andrew Kraemer
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://github.com/akraemer007}{\Large Andrew Kraemer}} & Email : \href{mailto:andrew.h.kraemer@gmail.com}{andrew.h.kraemer@gmail.com}\\
  Austin, Tx & Mobile : +1-847-644-1017 \\
  & Git : \href{http://github.com/akraemer007}{github.com/akraemer007}\\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cerebri AI}{Austin, Tx}
      {Data Scientist}{March 2018 - Present}
      \resumeItemListStart
        \resumeItem{Automotive Client Data Science Implementor}
          {Developed and implemented numerous sucessful models adding £250,000 for automotive clients using full data science stack - including data engineering, exploration, modeling, and productionization.}
        \resumeItem{Vehicle Affinity System}
          {Created hybrid model to identify customers most likely to purchase a particular model of car. Hybrid model used output of a DNN classfier to activate a Matrix Factorization model.}
        \resumeItem{Data Science Standards Lead}
          {Lead multi-channel team to research, disucss, and implement standards on the Data Science team. Standards include: custom packages for consistent data aquisition and cleaning, coding style standards, git workflow, and documentation guidelines}
      \resumeItemListEnd

    \resumeSubheading
      {Wellbe}{Madison, Wi}
      {Data Insights Guru}{August 2015 - August 2017}
      \resumeItemListStart
        \resumeItem{Business Intelligence Development}
          {Created and managed all analytics reports using Looker for on-demand visualizations.}
        \resumeItem{Data Engineering}
          {}
      \resumeItemListEnd

    \resumeSubheading
      {OptumRx}{Chicago, Il}
      {Finance Leadership Development Program}{June 2013 - June 2015}
      \resumeItemListStart
        \resumeItem{Portfolio Management}
          {Created models for portfolio hedging, portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Galvanize}{Austin, Tx}
      {Data Science Immersive}{October 2017 - January 2018}
    \resumeSubheading
      {Lawrence University}{Appleton, Wi}
      {Bachelor of Arts in Economics}{September 2009 - May 2013}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{What Exactly are We Turning Down For Again?}
      {A statistical analysis and modling of happiness of the Billboard top 100 music from 1955 to Present}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python (Pandas, Numpy, Sci-Kit Learn, PySpark), R (Tidyverse), SQL}
    }
    \item{
      \textbf{Technologies}{: Git, Linux, Spark, Azure, AWS, Looker, Tableau}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
